[Re] Chaos in a long-term experiment with a plankton community

### 2015-09-24 article/article.tex
original LE data added

The method for selecting the zeros to remove was unclear. In order to
reproduce this step, we removed the same data asin the original study,
by matching to the transformed data with zeros removed in the Ecology
Letters supplement Excel file mentioned above. All remaining
transformation steps were performed independently of this dataset. Our
reproduction of the transformed data closely matched the published
transformed data. \emph{This could result from us performing the
interpolation before the zero removal. Should correct this.}

@@

Correlations among species abundances presented in Table 1 of the
original article closely matched our reproduced correlations, calculated
from the transformed data with zeros removed.

\begin{longtable}[c]{@{}lcccccccccc@{}}
\caption{\label{tbl:table}Table caption }\tabularnewline
\toprule
& Bact & Harp & Ostr & N & P & Pico & Nano & Roti & Prot &
Cala\tabularnewline
\midrule
\endfirsthead
\toprule
& Bact & Harp & Ostr & N & P & Pico & Nano & Roti & Prot &
Cala\tabularnewline
\midrule
\endhead
Bact & & 0.03 & -0.24 *** & 0.05 & 0.18 *** & 0.03 & -0.17 *** & 0.3 ***
& -0.17 * & 0.22 ***\tabularnewline
Harp & & & 0.21 *** & -0.11 * & 0.03 & -0.09 & -0.06 & -0.05 & 0.14 &
0.01\tabularnewline
Ostr & & & & -0.16 ** & -0.06 & -0.06 & 0 & -0.05 & 0.18 * &
0.04\tabularnewline
N & & & & & 0.08 * & 0 & -0.02 & -0.04 & 0.03 & 0.04\tabularnewline
P & & & & & & -0.04 & 0.03 & 0.1 * & -0.02 & -0.08\tabularnewline
Pico & & & & & & & -0.17 *** & -0.03 & -0.21 * & 0.28 ***\tabularnewline
Nano & & & & & & & & -0.19 *** & 0.13 & -0.14 *\tabularnewline
Roti & & & & & & & & & -0.02 & -0.1 *\tabularnewline
Prot & & & & & & & & & & NA NA\tabularnewline
Cala & & & & & & & & & &\tabularnewline
\bottomrule
\end{longtable}

>>>>

The method for selecting the zeros to remove was unclear. In order to
reproduce this step, we removed the same data as in the original study,
by matching to the transformed data with zeros removed in the Ecology
Letters supplement Excel file mentioned above. All remaining
transformation steps were performed independently of this dataset. Our
reproduction of the transformed data closely matched the published
transformed data.

@@

Correlations among species abundances presented in Table 1 of the
original article closely matched our reproduced correlations, calculated
from the transformed data with zeros removed (figure
\ref{fig:corr_comp}). Deviations between the original and reproduced
correlations are relatively small (less than 0.072 units) and
infrequent. \textbf{These may have resulted from us removing zeros after
interpolation. Maybe we should check this.}

\begin{figure}[htbp]
\centering
\includegraphics{figures/correlation_comparison.pdf}
\caption{\label{fig:corr_comp}Comparison of calculated correlations
among species abundances in the original article and this reproduction.}
\end{figure}
